\documentclass[10pt,mathserif]{beamer}
\mode<presentation>{
\usetheme{Frankfurt}
\beamertemplateshadingbackground{red!5}{yellow!5}
\setbeamertemplate{navigation symbols}{}
\useinnertheme{rounded}
\useoutertheme{shadow}
\useoutertheme{infolines}
\usecolortheme[RGB={0,104,139}]{structure}%deepskyblue
\usefonttheme{serif}
}

\usepackage{graphicx}
%\usepackage{graphics,floatflt}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{wasysym}
\usepackage{helvet}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title[mutt/pine/pop/bash]{Terminal emailers: mutt}
\author[Dilawar \& Prashant]{Dilawar Singh. \&
			Prashant Dave\\
                        $\;$\\
Department of Electrical Engineering\\
Indian Institute of Technology Bombay}

\institute[IIT Bombay]{ }

\date[]{February 18, 2012}
\begin{document}
\bibliographystyle{alpha}

\begin{frame}
\maketitle
\end{frame}

\begin{frame}
 \frametitle{Outline}
\begin{enumerate}
 \item How to pop : getmail/fetchmail
\item msmtp for sending email 
\item mutt for reading (like pine)
\end{enumerate}
\end{frame}

\begin{frame}
Please download following files from github repository of\\
Dilawar Singh: https://github.com/dilawar

Go to MyPublic, and then to scripts and download:

\begin{itemize}
\item muttrc (the main one)
\item getmail for each of gpo and ee
\item msmtprc (for sending email)

\item python file mutt-ldap.py  (for using control-t for completing using ldap ids, then
   to choose)

\item ldap (perl script)
\end{itemize}

We prefer that ubuntu GNU/linux laptops be brought.\\

(cygwin too is fine, perhaps.)

\end{frame}

\end{document}

How to pop using getmail utility
(also fetchmail)

msmtp (for sending email ) like sendmail (perhaps)

mutt is for just reading. Just like pine.

mbox and maildir (two formats for storing files in our computer: for searching
purposes, etc differences)

crontab for scheduling getmail (for every half hour, etc) to get from 

python script to send queries to ldap (iitb allows this)
for getting gpo email-addresses

Dilawar's github repository

editor can be our preference. (vim/gedit/nano/emacs)

aliases of various email addresses

mailing list (one alias for several addresses, course participant/TAs)

html browsing (from within emailer)  (for extracting email)

can send content carefully typed in a txt file, and send that to several.
(tag several emails and respond including all emails into our response.)

pgp (for certificate signature)  (for more security)






-0----

from Dilawar's github

MyPublic/scripts

muttrc (the main one)
getmail for each of gpo and ee
msmtprc (for sending email)

python file mutt-ldap.py  (for using control-t for completing using ldap ids, then
   to choose)

ldap (perl script)

bring linux (ubuntu).
  We might be able to help *in the workshop* if you have cygwin (in case you have 
     windows.)

can also *leave* emails on the server. pop without deleting from server.
(server as main one.)

lee (wireless)

tunnelling for gmail (only due to iit firewall)

can overall *keep* emails on server, but can copy of ALL emails
or JUST ONE email on our computer. Can also delete all from THERE.


--------
pine is better for :
for mime-types (for certain files (like pdf, html, wmv, mov, automatically
understand which program to use, and NOT from file extension , but
header)

-----------

scripts: mail program, (without mutt-pine)
  

